Constrained, yet diverse: Phylogenetic and morphological filtering in epiphytic ferns

### 2019-08-15 ms/manuscript.Rmd
Fix figure numbers in output

```{r traits-used-image, fig.height = 7, fig.width = 7, fig.cap = "Examples of traits used in this study."}
knitr::include_graphics(here::here("images/Figure_3_1_traits_lowres.pdf"))
```

@@

```{r climate, fig.height = 4, fig.width = 7, fig.cap = "Microclimatic variables."}
climate_plot
ggsave(plot = climate_plot, filename = here::here("ms/Fig_1.pdf"), height = 4, width = 7, units = "in")
```

@@

```{r pca, fig.height = 6, fig.width = 6, fig.cap = "Trait PCA."}
pca_plot
ggsave(plot = pca_plot, filename = here::here("ms/Fig_2.pdf"), height = 6, width = 6, units = "in")
```

@@

```{r tree, fig.height = 8, fig.width = 6, fig.cap = "Traits on tree."}
traits_with_tree
ggsave(plot = traits_with_tree, filename = here::here("ms/Fig_3.pdf"), height = 8, width = 6, units = "in")
```

@@

```{r heatmap, fig.height = 4, fig.width = 6, fig.cap = "Variable importance scores."}
importance_heatmap
ggsave(plot = importance_heatmap, filename = here::here("ms/Fig_4.pdf"), height = 4, width = 6, units = "in")
```

@@

```{r cwm-div, fig.height = 4, fig.width = 7, fig.cap = "Community-weighted means."}
combined_cwm_plots
ggsave(plot = combined_cwm_plots, filename = here::here("ms/Fig_5.pdf"), height = 4, width = 7, units = "in")
```

@@

```{r comm-div, fig.height = 8, fig.width = 4, fig.cap = "Community diversity metrics."}
combined_comm_div_plots
ggsave(plot = combined_comm_div_plots, filename = here::here("ms/Fig_6.pdf"), height = 8, width = 4, units = "in")
```

>>>>

```{r traits-used-image, fig.height = 9, fig.width = 6, fig.cap = "Examples of traits used in this study."}
knitr::include_graphics(here::here("ms/Fig_1.pdf"))
```

@@

```{r climate, fig.height = 4, fig.width = 7, fig.cap = "Microclimatic variables."}
climate_plot
ggsave(plot = climate_plot, filename = here::here("ms/Fig_2.pdf"), height = 4, width = 7, units = "in")
```

@@

```{r pca, fig.height = 6, fig.width = 6, fig.cap = "Trait PCA."}
pca_plot
ggsave(plot = pca_plot, filename = here::here("ms/Fig_3.pdf"), height = 6, width = 6, units = "in")
```

@@

```{r tree, fig.height = 8, fig.width = 6, fig.cap = "Traits on tree."}
traits_with_tree
ggsave(plot = traits_with_tree, filename = here::here("ms/Fig_4.pdf"), height = 8, width = 6, units = "in")
```

@@

```{r heatmap, fig.height = 4, fig.width = 6, fig.cap = "Variable importance scores."}
importance_heatmap
ggsave(plot = importance_heatmap, filename = here::here("ms/Fig_5.pdf"), height = 4, width = 6, units = "in")
```

@@

```{r cwm-div, fig.height = 4, fig.width = 7, fig.cap = "Community-weighted means."}
combined_cwm_plots
ggsave(plot = combined_cwm_plots, filename = here::here("ms/Fig_6.pdf"), height = 4, width = 7, units = "in")
```

@@

```{r comm-div, fig.height = 8, fig.width = 4, fig.cap = "Community diversity metrics."}
combined_comm_div_plots
ggsave(plot = combined_comm_div_plots, filename = here::here("ms/Fig_7.pdf"), height = 8, width = 4, units = "in")
```
